
\chapter{Voting}

\section{Voting Overview}

	\begin{enumerate}
		\item All brothers eligible to vote must vote.

		\item Only active brothers who are not on \gls{prob} or \gls{fin-probation} are eligible to vote.

		\item Brothers must be present for all of the discussion on a motion in order to be eligible to vote on that motion.\label{voting-present} 

		\item A brother not required to pay local dues is ineligible to vote. %This is for people on co-op

		\item Unless specified in Article IV section B, the method of voting will be by a show of hands. 

	\end{enumerate}


\section{Procedure}
\label{procudure}
	\begin{enumerate}
		\item The following votes will be performed by ballot:
			\begin{enumerate}
				\item New Members for Initiation 
				\item Officer Elections 
				\item To overturn an \gls{ec} Interpretation of the bylaws (\hyperref[interpretation]{Article I, \autoref*{interpretation}}) 
				\item At a suspension trial
                \item To retain a candidate who was not initiated the previous semester
			\end{enumerate}

		\item Balloting
		\begin{enumerate}

			\item The Second Guard and the Chaplain will collect and count the ballots.

			\item The chaplain will confirm the count and repeat the results to the presiding officer.

            \item No brother may count the ballots for a matter related to himself.

            \item In the case of absense, conflict of interest, or at the discretion of the chair, the chair may appoint a brother to collect and count the ballots.

		\end{enumerate}

		\item New Members for Initiation
		\begin{enumerate}
			\item Balloting on New Members for Initiation will be in accordance with the \gls{ibl} of Theta Chi Fraternity, Article VI, Section 4, paragraph d.

			\item New Members must be approved by a $\frac{3}{4}$ vote of the active chapter to be initiated.
            \begin{enumerate}
                \item This may be reduced for the duration of a single chapter meeting to an \gls{abs-maj} vote by a \gls{simp-maj} vote.
            \end{enumerate}
		\end{enumerate}

		\item Officer Elections
		\begin{enumerate}
			\item Officers will be elected by \gls{simp-maj} vote.

			\item In the case that no nominee receives a \gls{simp-maj}, there will immediately be another vote between all candidates who received the two highest counts of votes.
            \item Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for CAB interviews. %CAB needs time to interview 
		\end{enumerate}

	\end{enumerate}
