\chapter{Officer Selection and Duties}

\section{Terms of Office}
	\begin{enumerate}
		\item All elected offices will have yearly terms except Standards Board Justice.
			\begin{enumerate}

				\item Each Standards Board Justice will be elected to serve until resignation, ineligibility, removal from office, or graduation (\hyperref[justice-term]{Article XII, Section B, \autoref*{justice-term}}).
			\end{enumerate}
		\item The President will appoint all appointed officers subject to a \gls{simp-maj} vote of the chapter. \label{appointed-approval}

		\item Appointed positions will have semesterly terms except for OX Roast Chair, and Community Standards Chair.

		\item The Recruitment Chair and Public Relations Chair will serve from the end of the first Rush period after election or appointment through the first Rush period after the election or appointment of a new officer.
	\end{enumerate}

\section{Nominations}
	\begin{enumerate}
		\item Nominations will be opened at least one week before elections.
		\item All members, in order to be eligible for nomination, must be in good standing with the University and the International Fraternity and must not be on \gls{fin-probation}.
	\end{enumerate}


\section{Elections}
	\label{elections}
	\begin{enumerate}
		\item Officers will be elected in accordance with the \gls{ibl} Article V, Section 3.
		\item Nominations must be closed in order to elect an officer.
		\item For each elected position, excluding Standards Board Justices, the election will proceed as such:
			\begin{enumerate}
				\item For each candidate:
					\begin{enumerate}
						\item Candidates will be allowed speeches following
						these rules:
							\begin{enumerate}
								\item Other candidates will leave the room.
								\item Candidates will be allowed not less than
								three minutes to speak.
							\end{enumerate}
						\item The chapter will be allowed to ask the
						candidate questions following these rules:
							\begin{enumerate}
								\item The chapter will be allowed not less
								than two minutes to question.
								\item Any time not used by a candidate for his
								speech will be allowed for questions.
							\end{enumerate}
					\end{enumerate}
				\item The chapter will discuss the candidates subject to the
				following rules:
					\begin{enumerate}
						\item All candidates will leave the room.
						\item The chapter will be allowed not less than five
						minutes to discuss.
						\item If the candidate is elected by white ballot, this section does not apply.
					\end{enumerate}
				\item Candidates will be allowed to vote in the election in direct exception to the above \hyperref[voting-present]{Article IV, Section A, \autoref*{voting-present}}.
			\end{enumerate}
    \item Standards Board elections will proceed as such:
        \begin{enumerate}
            \item There will be one election for all open Standards Board positions.
	    \item The election will be held by ranked-choice voting system.
            \item Each ballot must include a chosen nominee for each opening.
            \item Any nominee receiving a \gls{simp-maj} or \gls{plur} of votes is elected to an open position.
	    	\begin{enumerate}
			\item The First Guard will be responsible for the creation of a Standards Board Plan.
		\end{enumerate}
            \item If all open positions are not filled, repeat this process.
            \item In the case of electing multiple Standards Board justices, the nominees will be allowed to hear the speeches of the other candidates in exception of Article V, Section 3, Item (a), point i, subpoint A.
        \end{enumerate}
    \item If an elected position should become vacant:
			\begin{enumerate}
				\item The President will appoint an interim officer, preferably a brother who has held the office before.
				\item Nominations for the open position will take place at the next regularly scheduled chapter meeting.
				\item The week following the opening of nominations, elections will proceed as defined above in \hyperref[elections]{Article V, \autoref*{elections}}.
			\end{enumerate}
	\end{enumerate}

\section{Elected Officers and Their Duties}
	\begin{enumerate}
		\item President
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph a.
				\item Serves as a liaison between the chapter and the community.
				\item Attends all \gls{ifc} and Greek Life Office functions expected of the President.
				\item Attends all \gls{cab} meetings.
				\item Responsible for the overall completion of \gls{pytte}.
                \item A candidate for the position of President must be interviewed by the CAB prior to the
election. A simple majority vote of the CAB may veto that candidate. This veto can be overruled
by a supermajority vote of the chapter. Failure for CAB to meet with a candidate prior to
elections will be interpreted as CAB waiving their right to interview the candidate.
				\item Serves as a member of \gls{ec}.
				\item Must live in the house.
			\end{enumerate}

		\item Vice President
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph b.
				\item Serves as Parliamentarian for the chapter, Standards Board, and is responsible for all committees.
				\item Maintains the chapter's local bylaws. %that's these, dear reader!
                		\item Ensures legislation records are up to date.
				\item Adds all permanent legislation to the appropriate appendix as outlined in \hyperref[appendices]{Article I, \autoref*{appendices}}.
				\item Adds EC Interpretations to the Appendices.
				\item Appoints active members to committees at the beginning of each semester.
				\item Assigns living space as outlined in \hyperref[housing]{Article VII, \autoref*{housing}}.
				\item Serves as chair of the Bylaw Revision Committee as outlined in \hyperref[bylaw-revisions]{Article IX, \autoref*{bylaw-revisions}}.
				\item Responsible for the Leadership portion of \gls{pytte}.
				\item Serves as chair of \gls{ec} and represents it to the chapter.
				\item Serves as chair of the \gls{ccc}.
				\item May make Ad Hoc Committees at their discretion as defined in \hyperref[adhoccom]{Article V, Section G, \autoref*{adhoccom}}.
				\item Must live in the house.
			\end{enumerate}

		\item Vice President of Health and Safety
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph c.
				\item Plans and oversees a yearly community outreach event regarding health and safety.
				\item Serves as a liaison between the chapter and community health services.
				\item Organizes events on 7 topics, 2 of which are available to the greater public, on Health and Safety for the chapter per academic year.
				\item Maintains house medical kit.
				\item Responsible for the Citizenship portion of \gls{pytte}.
				\item Serves as a member of \gls{ec}.
				\item Serves as chair of the Health and Safety Committee.
				\item Must live in the house.
			\end{enumerate}

		\item Secretary
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph d.
				\item Records attendance and enforces the standards for attendance in \hyperref[attendance]{Article III, \autoref*{attendance}}.
				\item Serves as Secretary of \gls{ec}
				\item Collects all legislation, Bylaw amendments, and Officer Reports according to \hyperref[legislation-time]{Article II, \autoref*{legislation-time}} and \hyperref[bylaw-time]{Article I, Section B, \autoref*{bylaw-time}}.
				\item Sets the agenda for chapter meetings according to the \gls{ibl} Article V, Section 8, paragraph d.
				\item Maintains the mailbox and mail closet.
				\item Will create a contact list for the chapter which includes contact information of brothers, advisors, Greek Life, and emergency services.
				\item Handles registration of Pledges, requests for initiation, and the recording of new initiates.
				\item Serves on \gls{ccc}.
				\item Must live in the house.
			\end{enumerate}

		\item Treasurer \label{treasurer-duties}
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph e.
				\item Is accountable to the Alumni Corporation.
				\item Collects all fees, dues, and fines.
				\item Records all transactions made by the chapter.
				\item Will provide a written report at the request of any brother. The report will include all payments paid out, all monies received, current bank account balances, and budget updates.
				\item Keeps private all individual account balances except from the brother whose account it is and \gls{ec}.
				\item Issues enumerated bills for all brothers and New Members at least three times a semester unless otherwise decided by the chapter.
				\item Announces the names of all members on \gls{fin-probation} at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
				\item Will create a budget following the process outlined in \hyperref[budget]{Article VI, \autoref*{budget}}.
				\item Ensures compliance with the General Rules for chapter finances outlined in \hyperref[fin-rules]{Article VI, \autoref*{fin-rules}}.
				\item Will propose a housing contract to the chapter by the last chapter meeting of each semester with a final version to be approved at the first chapter meeting of the next semester.
				\item Will ensure that all brothers living in the house have signed a housing contract by the second chapter meeting of each semester.\label{housing-contract}
				\item Maintains an emergency fund of no less than \$3000 and can withdraw money from the fund only with the authorization of two of the three highest officers. %Example: The chapter is in fucking problems.
				\item Will meet with the Alumni Financial Advisor at least twice each semester.
				\item Will file taxes at least two weeks before the filing deadline each year.
				\item Will ensure that taxes will be reviewed by the \gls{cab} financial advisor, alumni housing corporation financial advisor, and \gls{ec} no later than one month before the filing deadline.
				\item Will send taxes by certified mail, and will distribute this certification to the \gls{cab} financial advisor, alumni housing corporation financial advisor, and \gls{ec}.
				\item Will retain a physical and electronic backup of financial records for no fewer than five years.
                		\item Maintain a changelog of the budget.
               		 	\item Give a monthly financial report to the chapter and deliver the report to CAB.
               		 	\item The Treasurer cannot be elected or appointed to a position which has permission
to spend from the budget.
				\item Cannot be elected to another position during their term.
				\item A candidate for the position of Treasurer must be interviewed by the CAB prior to the
election. A simple majority vote of the CAB may veto that candidate. This veto can be overruled
by a supermajority vote of the chapter. Failure for CAB to meet with a candidate prior to
elections will be interpreted as CAB waiving their right to interview the candidate.
				\item Serves as a member of \gls{ec}.
				\item Must live in the house.
			\end{enumerate}

		\item Marshal
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph f.
				\item Will submit a plan as legislation for their office by the first chapter meeting of the semester of their term.
				\item Will reserve a location for initiation.
                		\item Will organize a bid acceptance dinner and the bid acceptance ceremony.
				\item Responsible for the Ritual portion of \gls{pytte}.
				\item Serves as a member of \gls{ec}.
				\item Must live in the house.
			\end{enumerate}

        	\item Recruitment Chair
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph l
				\item Assumes responsibility for directing the recruitment process.
				\item Chairs the Recruitment Committee.
				\item Will run a recruitment workshop each semester.
				\item Will present a Rush calendar to the chapter by Initiation.
				\item Will be responsible for any Rush period that they have planned, including those after their term.
				\item Confirms and tracks the attendance of each brother at Rush events (\hyperref[rush-attend-std]{Article XI, Section B, \autoref*{rush-attend-std}}).
				\item Serves as a member of \gls{ec}. \label{recruit-chair-term}
                		\item Must live in the house.
			\end{enumerate}

		\item Scholarship Chair \label{schol-chair-duties}
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph i.
				\item Performs all duties specified by the Greek Life Office, \gls{ifc}, and the University.
				\item Will prepare a written \gls{schol-program}, submit it to the Office of Greek Life, and pass it as legislation in chapter by the 2nd chapter of their term, containing the following:
				\begin{enumerate}
					\item A plan for the creation of Scholarship contracts for all brothers.
					\item A plan for ensuring the chapter house is an environment conducive to studying.
					\item A plan for providing incentives for academic achievements.
				\end{enumerate}
				\item Will present the \gls{schol-program} to new members.
				\item Works with the Marshal to promote academic well-being among New Members.
                		\item Organizes a formal scholarship dinner to recognize achievement about scholarship within the chapter.
				\item Will arrange at least one program per semester with a speaker who will talk to the chapter about scholarship or an issue relating to scholarship.
				\item Will ensure all brothers are a part of at least one non-greek club or activity.
				\item Attends monthly meetings with the Greek Community Educational Consultants in accordance with \gls{cwru} Greek Communtiy Standards.
				\item Ensures that member scholarship standards are enforced (\hyperref[member-schol-stds]{Article X, \autoref*{member-schol-stds}}).
				\item Responsible for the Scholarship portion of \gls{pytte}.
                \item Serves as chair for the Scholarship Committee.
                \item Serves on \gls{ec}.
                \item Must live in the house.
			\end{enumerate}


		\item Chaplain
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph g.
				\item Handles conflict resolution in the chapter.
				\item Organizes and mediates round table discussions on contentious issues between brothers.
				\item Must live in the house.
			\end{enumerate}

		\item Historian
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph h.
				\item Assists alumni relations chair with the alumni database.
				\item Ensures that pictures are taken at chapter events.
				\item Will make a yearly scrapbook for the semester that they serve with the assistance of the previous historian.
				\item Manages the chapter's online photo and video galleries jointly with the PR Chair.
				\item Works with the house manager to ensure that the composites are displayed correctly.
				\item Maintains and updates the photos around the house.
				\item Maintains the chapter museum.
			\end{enumerate}

		\item First Guard
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph j.
				\item Assists Marshal in planning and executing initiation and prepares the chapter for it.
				\item Serves as Arbiter of Standards Board.
				\item Prepares the chapter room for meetings.
				\item Will enforce reasonable dress in the chapter room as stated in \hyperref[chapter-dress]{Article III, Section D, \autoref*{chapter-dress}}.
			\end{enumerate}

		\item Second Guard
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph k.
				\item Serves as Scribe of Standards Board.
				\item Assists the first guard in preparing the chapter room for meetings.
			\end{enumerate}
		\item Standards Board Justice
			\begin{enumerate}
				%This is a duplicate of the duties defined in Article 12: Standards Board. If one is changed, the other should be as well.
				\item Hears and rules on all cases brought before Standards Board as defined in \autoref{stds-board}.
				\item Attends all meetings of Standards Board.
				\item Keeps confidential all matters related to judicial proceedings.
				\item Treats all brothers and New Members fairly, impartially, and consistently.
			\end{enumerate}


	\end{enumerate}

\section{Appointed Positions}
	\begin{enumerate}
                \item Executive Council Member at Large
			\begin{enumerate}
				\item Must have previously served on \gls{ec} for a full term.
				\item Must not hold another \gls{ec} position.
				\item Assists and advises \gls{ec}.
			\end{enumerate}

		\item Public Relations Chair
			\begin{enumerate}
				\item Serves as chair of the Public Relations Committee (\hyperref[op-comm]{Article V, Section G, \autoref*{op-comm}}).
				\item Works with the Public Relations Committee to create PR for the public events of the chapter at the request of other chairs.
				\item Maintains the chapter social media pages and accounts.
				\item Serves as a member of \gls{ccc}.
			\end{enumerate}

		\item Social Chair
			\begin{enumerate}
				\item Organizes \glspl{social}.
				\item Ensures that all \glspl{social} run in accordance with all University, Greek Life, \gls{ifc}, \gls{nic}, and IHQ regulations and policies.
				\item Serves as chair of the Social Committee (\hyperref[standing-comm]{Article V, Section G, \autoref*{standing-comm}}).
				\item Will attend all \gls{ifc} Social Chair meetings.
				\item Serves as a member of \gls{ccc}.
			\end{enumerate}

		\item Alumni Relations Chair
			\begin{enumerate}
				\item Collects materials for and edits the Alumni Newsletter with the help of the Alumni Corporation and sends out the ALumni newsletter before the lasta day of classes.
				\item Maintains the alumni database.
				\item Serves as chair of the Alumni Relations Committee (\hyperref[op-comm]{Article V, Section G, \autoref*{op-comm}}).
				\item Organizes the Alumni Ceremony at the end of the semester in which they serve.
				\item Serves as a member of \gls{ccc}.
			\end{enumerate}

		\item Membership Development Chair
			\begin{enumerate}
				\item  Serves as chair of the Membership Development Committee.
				\item Will plan and carry out at least one event or program in each of the following categories: 
					\begin{enumerate}
						\item Mental well-being
						\item Physical well-being
						\item Professional development
						\item Recreation
				\item Serves as a member of \gls{ccc}.
			\end{enumerate}

		\item Service Manager
			\begin{enumerate}
				\item Serves as chair of the Philanthropy committee.
				\item Ensures that the chapter meets Greek Life goals for philanthropy.
				\item Informs the chapter of philanthropy.
				\item Serves as a member of \gls{ccc}.
			\end{enumerate}

		\item Service Chair
			\begin{enumerate}
				\item Ensures that the chapter meets Greek Life goals for service.
				\item Informs the chapter of service opportunities.
				\item Sets individual service requirements for each brother for each semester.
				\item Brings brothers up for standards for not meeting service requirements.
				\item Serves as a member of \gls{ccc}.
			\end{enumerate}

		\item House Manager
			\begin{enumerate}
				\item Will live in the house.
				\item Assumes responsibility for the maintenance of the fraternity residence and surrounding property.
				\item Oversees and assumes responsibility for all property of the fraternity including repair and replacement of equipment.
				\item Creates, implements, and monitors a parking lot program to be approved by the treasurer.
				\item Serves as a member of \gls{ccc}.
			\end{enumerate}

		\item Detail Manager
			\begin{enumerate}
				\item Will pass a house and kitchen detail plan as legislation by the first chapter meeting of the semester in which they serve. The plan must contain provisions for the assessment of fines for delinquency in details.
				\item Assigns weekly house details and weekly kitchen details.
				\item Will be responsible for the direction of all \glspl{special-detail}, which may be called at their discretion.
			\end{enumerate}

		\item Food Steward
			\begin{enumerate}
				\item Works with a chef or catering service to maintain a brotherhood meal plan.
				\item Ensures the service chosen for the meal plan is paid for according the agreement with the chef or catering service.
				\item Must be on the meal plan.
				\item Works with the Detail Manager to keep public areas in the kitchen clean and ensure proper storage of food.
				\item Assigns cabinet and fridge space to in-house brothers.
				\item Must live in the house.
			\end{enumerate}

		\item Risk Manager
			\begin{enumerate}
				\item Performs all duties specified in the \gls{ifc} Bylaws, Article IX (\href{https://community.case.edu/greeklife/interfraternal-bylaws/}{IFC Bylaws Webpage}).
				\item Schedules \gls{smarrt} or similar presentations at the request of the Greek Like Office.
				\item Ensures compliance with all Greek Life, University, \gls{ihq}, and \gls{nic} guidelines and policies.
				\item Attend Office of Greek Life risk manager meetings.
			\end{enumerate}

		\item Awards Chair
			\begin{enumerate}
				\item Leads a committee to fill out Greek Life and \gls{ihq} awards that are due in their term.
				\item Serves as a member of \gls{ccc}.
				\item Works with the President to fill out Chapter Standards by the fall deadline.
				\item Maintains a system for collecting documentation which includes, but is not limited to the following:
					\begin{enumerate}
						\item All events and activities of the chapter.
						\item Accomplishments of chapter officers (i.e. service hours and recruitment numbers)
					\end{enumerate}
			\end{enumerate}

		\item Greek Games Chair
			%Informally referred to as the "God Emperor of Greek Week".
			\begin{enumerate}
				\item Organizes the chapter's participation in Greek Week.
				\item Attends Greek Week Chair meetings sponsored by the Greek Week Steering Committee.
				\item Appoints brothers to captain Greek Week events.
			\end{enumerate}

		\item Interfraternity Congress Representative
			\begin{enumerate}
				\item Represents the chapter at \gls{ifc} meetings.
				\item Must have been a brother for at least one full semester.
			\end{enumerate}

		\item Librarian
		\begin{enumerate}
			\item Sits on the Scholarship Committee.
			\item Manages house library and book collections.
		\end{enumerate}

		\item OX Roast Chair
			\begin{enumerate}
				\item Must serve on Alumni Relations Committee.
				\item Plans the annual OX Roast event with the alumni to be held in the fall semester.
				\item Will be appointed after OX Roast to serve until the next OX Roast.
			\end{enumerate}

		\item Temporary Chairs
			\begin{enumerate}
				\item May be appointed by the President to be in charge of specific events. Examples include DAMAGE Chair, Formal Chair, and Master of the Universe.
			\end{enumerate}

\end{enumerate}

\section{Executive Council}
	\begin{enumerate}
		\item Membership
			\begin{enumerate}
				\item \Gls{ec} will be composed of the following:
					\begin{enumerate}
						\item President
						\item Vice President
						\item Vice President of Health and Safety
						\item Secretary
						\item Treasurer
						\item Marshal
						\item Recruitment Chair
                        			\item Scholarship Chair
						\item Executive Council Member at Large
					\end{enumerate}

			\end{enumerate}

		\item Purpose, Duties, and Powers
			\begin{enumerate}
				\item Interprets the bylaws as outlined in \hyperref[interpretation]{Article I, \autoref*{interpretation}}.
				\item Serves as an executive body.
				\item Guides the chapter in emergencies.
				\item Reviews excuses for chapter meetings and other chapter events.
					\begin{enumerate}
					\item In evaluating excuses, the EC shall adhere to the standards set in the
					Acceptable Excuses Plan. Said Acceptable Excuses Plan shall consist of the following:
						\begin{enumerate}
							\item specifically what is an acceptable excuse, with examples
							\item specifically what is not an acceptable excuse, with examples
							\item the number of unexcused absences \slash personal days \slash “no questions asked” missed chapters allowed per semester before taken to standards board
						\end{enumerate}

					\item The Acceptable Excuses Plan shall be distributed to the chapter one week before retreat at the beginning of every semester and approved at retreat, with any necessary amendments, as a piece of temporary legislation valid for one semester.
				\end{enumerate}
				\item Reviews \glspl{req-def} (\hyperref[req-def]{Article VI, \autoref*{req-def}}).
				\item Passes Executive Edicts as defined in \hyperref[exec-edict]{Article II, Section D, \autoref*{exec-edict}}
				\item Suspends portions of the Bylaws subject to chapter approval as defined in \hyperref[suspend-bylaws]{Article I, \autoref*{suspend-bylaws}}.
				\item Reviews appeals to \gls{academic-probation} as defined in \hyperref[schol-appeals]{Article X, \autoref*{member-schol-stds}}.
				\item Meet with respective \gls{cab} member once a month.
				\item Appoints appointed positions.
			\end{enumerate}

		\item Voting
			\begin{enumerate}
				\item Voting Members
					\begin{enumerate}
						\item Vice President
						\item Vice President of Health and Safety
						\item Secretary
						\item Treasurer
						\item Marshal
						\item Recruitment Chair
                        \item Scholarship Chair
					\end{enumerate}
				\item Quorum will consist of at least five members, at least four of whom must be voting members.
				\item All votes are decided by an \gls{abs-maj} of \gls{ec}.
                \begin{enumerate}
                    \item The President will have a vote in case of a tie.
                \end{enumerate}
			\end{enumerate}
		\item Procedure
			\begin{enumerate}
				\item \gls{ec} is chaired by the Vice President.
				\item \gls{ec} will meet weekly while school is in session.
				\item \gls{ec} will admit any brother or candidate unless the meeting is declared closed by the Vice President or an \gls{abs-maj} of \gls{ec}.
					\begin{enumerate}
                        			\item \gls{ec} may admit any guest to closed EC by an \gls{abs-maj} vote.
						\item \gls{ec} meetings will be closed to non-\gls{ec} members in situations that require discussing private or emergency matters such as \glspl{req-def}.
					\end{enumerate}
				\item The Vice President will serve as the representative of \gls{ec} to the chapter.
			\end{enumerate}
	\end{enumerate}

\section{Committees}
\label{committees}

\begin{enumerate}
	\item Every brother must be a member of at least one Standing and one Operational Committee.
    \begin{enumerate}
        \item If a brother misses three meetings of any one of their assigned committees without obtaining and approved excuse from that committee's chair, that committee's chair may bring that brother up for standards of behavior unbecoming of a brother.
        \item committee meetings scheduled less than five days in advance cannot be counted towards the absences above.
    \end{enumerate}
	\item The chapter will have the following committees:
		\begin{enumerate}
			\item Standing Committees \label{standing-comm}
				\begin{enumerate}
					\item The Standing Committees of the chapter will include:

						\begin{enumerate}
							\item Recruitment Committee
							\item Public Relations Committee
							\item Health and Safety Committee
							\item Social Committee
						\end{enumerate}

					\item All Standing Committees will do the following:
						\begin{enumerate}
							\item Meet at least once every two weeks as directed by their chair.
							\item Assist the chair in the discharge of their duties.
							\item Create a set of goals for the committee at the first meeting of the committee.
							\item Work toward the goals of the committee.
						\end{enumerate}
				\end{enumerate}

			\item Operational Committees \label{op-comm}
				\begin{enumerate}
					\item The Operational Committees of the chapter will include:

						\begin{enumerate}
							\item Alumni Relations Committee
							\item Member Development Committee
							\item Scholarship Committee
							\item Philanthropy and Service Committee
						\end{enumerate}

					\item All Operational Committees will do the following:
						\begin{enumerate}
							\item Meet at least once every four weeks as directed by their chair.
							\item Assist the chair in the discharge of their duties.
							\item Create a set of goals for the committee at the first meeting of the committee.
							\item Work toward the goals of the committee.
						\end{enumerate}
				\end{enumerate}

			\item Budget Committee
				\label{budget-committee}
				\begin{enumerate}
					\item Purpose and Duties
						\begin{enumerate}
							\item To create a budget for the chapter for the next year pursuant to \hyperref[budget]{Article VI, \autoref*{budget}}.
							\item To examine any financial issues of the chapter.
						\end{enumerate}

					\item Membership
						\begin{enumerate}
							\item The Treasurer will serve as chair of the Budget Committee.
							\item The body of the committee will be selected by the treasurer.
						\end{enumerate}

					\item Procedure
						\begin{enumerate}
							\item The committee will be created and convened during the budgeting process outlined in \hyperref[budget]{Article VI, \autoref*{budget}}.
							\item The committee may meet at other times to examine the finances of the chapter at the direction of \gls{ec}.
						\end{enumerate}
				\end{enumerate}

			\item Mandatory Bylaw Revision Committee
				\begin{enumerate}
					\item The Mandatory Bylaw Revision Committee will function in accordance with \hyperref[bylaw-revisions]{Article IX, \autoref*{bylaw-revisions}}.
				\end{enumerate}


			\glsreset{ccc}

			\item \gls{ccc}
				\begin{enumerate}
					\item Purpose
						\begin{enumerate}
							\item To facilitate communication between committee chairs.
							\item To keep the Vice President informed of committee business.
							\item To help the Vice President ensure that committees are performing all necessary duties.
						\end{enumerate}
					\item Membership
						\begin{enumerate}
							\item The Vice President will serve as the Chair of the \gls{ccc}.
							\item The Chairs of all Standing and Operational Committees will be members.
							\item Other brothers may be added to the committee at the Vice President's discretion.
						\end{enumerate}
					\item Procedure
						\begin{enumerate}
							\item The committee will meet weekly while school is in session.
							\item The Vice President will evaluate progress toward committee goals.
						\end{enumerate}
				\end{enumerate}

		\end{enumerate}

	\item Ad Hoc Committees
		\begin{enumerate}
			\item The Vice President has the power to make other committees at their discretion. \label{adhoccom}
		\end{enumerate}
\end{enumerate}


