\chapter{Expectations of Brothers}
\label{expectations-bhood}

\section{Code of Conduct}
	\begin{enumerate}
		\item No brother will reveal the secrets of the fraternity to anyone who is not an initiated member of Theta Chi Fraternity.
		\item All brothers will obey all federal, state, and local laws.
		\item All brothers will obey all University regulations and \gls{ifc} Constitution and Bylaws.
		\item All brothers will obey the \gls{ibl}.
		\item All brothers will obey the local bylaws and the provisions of the lease on the fraternity house.

	\end{enumerate}

\section{Standards of Brotherhood}

	\begin{enumerate}
		\item Financial
			\begin{enumerate}
				\item Brothers will abide by the financial obligations outlined in \hyperref[fin-obligations]{Article VI, \autoref*{fin-obligations}}.
			\end{enumerate}

		\item Rush
			\begin{enumerate}
				\label{rush-attend-std}
				\item Brothers will \gls{attend} an amount of Rush events as specified by the Rush Plan.
			\end{enumerate}

		\item Social
			\begin{enumerate}
				\item Brothers will \gls{attend} a majority of \glspl{social} each semester unless they are on \gls{academic-probation}.
				\item Brothers not on \gls{academic-probation} will be involved in at least one non-greek campus student organization.
			\end{enumerate}

		\item Scholarship
			\begin{enumerate}
				\item Brothers will abide by the scholarship standards described in \hyperref[member-schol-stds]{Article X, \autoref*{member-schol-stds}}.
			\end{enumerate}

		\item Service
			\begin{enumerate}
				\item Brothers will complete the service hours assigned to them by the Philanthropy and Service Chairman.
			\end{enumerate}

		\item Chapter Events
			\begin{enumerate}
				\item When an event is declared an \gls{official-chapter-event} by \gls{ec}, all members must \gls{attend} it unless excused by \gls{ec}. A missed \gls{official-chapter-event} that is not excused will count as an unexcused mandatory event
					\begin{enumerate}
						\item Missing a mandatory event without an accepted excuse will count as unexcused.

						\item A brother who has three unexcused mandatory events in a row must be brought up for standards by the Secretary with the possibility of suspension

						\item A brother who has three unexcused mandatory events throughout the semester will be staggard.

						\item A brother who has four unexcused mandatory events throughout the semester will be placed on probation until the end of the semester.

						\item A brother who has seven or more unexcused mandatory events throughout the semester will be brought up for standards by the Secretary with the possibility of suspension.
					\end{enumerate}

				\item Brothers will attend chapter meetings as outlined in \hyperref[attendance]{Article III, \autoref*{attendance}}.
			\end{enumerate}

		\item Committees
			\begin{enumerate}
				\item Brothers will be active members of committees and abide by all relevant bylaws pertaining to the roles and responsibilities of committee members, as detailed in \hyperref[committees]{Article V, \autoref*{committees}}.
				\item Brothers will attend assigned committee meetings as outlined in Article V.G.1.
			\end{enumerate}

	\end{enumerate}
	
\section{Considerations for Potential New Members}
	\begin{enumerate}
		\item When issuing bids to potential new members, the chapter will take into account their behavior, especially towards non-brothers, and ensure that it is consistent with our expectations of brothers.
	\end{enumerate}
