\chapter{Bylaw Structure}

\section{Bylaws as Pertaining to the International Fraternity}

	\begin{enumerate}
		\item The Bylaws of Beta Nu Chapter of Theta Chi Fraternity are adopted as provided for in the \gls{ibl} of Theta Chi Fraternity (Article V, Section 1).

		\item The bylaws of this chapter will be superseded by the \gls{ibl} of Theta Chi Fraternity.
	\end{enumerate}

\section{Amendments}
\label{bylaw-amendments}
	\begin{enumerate}
		\item All proposed amendments to these Bylaws will specify in the motion that they are amendments.

		\item A proposed Amendment may not be voted on unless it has been brought up at least one chapter meeting before or has been available for inspection for at least six days.

		\item A proposed amendment must receive a \gls{super-maj} vote for ratification.

	\end{enumerate}

\section{Suspension}
\label{suspend-bylaws}
	\begin{enumerate}
		\item Portions of the bylaws may be suspended by \gls{super-maj} vote of the chapter.
		\item Motions to suspend a portion of the bylaws must contain:
			\begin{enumerate}
				\item To whom the suspension applies.
				\item The time period during which the suspension applies.
				\item The portion to be suspended.
			\end{enumerate}
		\item The \gls{ec} may issue an \gls{ex-ed} by \gls{abs-maj} vote in the case of an emergency. \label{executive-edict}
			\begin{enumerate}
				\item The \gls{ex-ed} will be proposed to the chapter at the next chapter meeting with \gls{qorm} by the Vice President.
				\item The \gls{ex-ed} must be approved by the chapter by a \gls{super-maj} vote in order for the
\gls{ex-ed} to remain in effect after the chapter in which it was voted upon. 
			\end{enumerate}
	\end{enumerate}

\section{Interpretation}
	\label{interpretation}
	\begin{enumerate}
		\item \Gls{ec} will have the power to interpret these Bylaws.

		\item Any brother may bring EC Bylaw Interpretation \glspl{grieve}, in writing, to \gls{ec}.

		\begin{enumerate}
			\item All \glspl{grieve} brought to \gls{ec} will at all times be confidential.

			\item The results of the \gls{grieve} will be announced to the chapter at the next chapter meeting.

			\begin{enumerate}
				\item \gls{ec} interpretation is subject to overrule by a \gls{super-maj} vote of the active chapter.

				\begin{enumerate}
					\item Voting to overrule an \gls{ec} interpretation of these Bylaws will be done by \gls{balloting}.
				\end{enumerate}
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}

\section{Glossary}
	\begin{enumerate}
		\item All highlighted terms are defined in the Glossary section. 
		\item The Glossary is a binding section of the bylaws. 
		\item Amendments to the Glossary will follow the procedure in \hyperref[bylaw-amendments]{Article I, \autoref*{bylaw-amendments}}.
	\end{enumerate}
	
\section{Appendices}
	\label{appendices}
	\begin{enumerate}
		\item This document will have the following appendices:
			\begin{enumerate}
				\item \gls{ec} Interpretations
					\begin{enumerate}
						\item Will contain a record of \gls{ec} interpretations of the local bylaws.
						\item Interpretations that refer to deprecated parts of the local bylaws may be removed at the discretion of the Vice President.
						\item Items may be added to this appendix by the Vice President.
					\end{enumerate}
				\item Trial Precedents
					\begin{enumerate}
						\item Will contain the choice of trial and results of all Trial Hearings for the purpose of establishing precedent.
						\item All parties will remain anonymous.
						\item Items will be added to this appendix by the Arbiter or Parliamentarian of Standards Board and will include the date that the decision was made.
						\item Items that are over five years old may be removed at the discretion of the Arbiter or Parliamentarian of Standards Board.
					\end{enumerate}
				\item Permanent Legislation
					\begin{enumerate}
						\item Will contain all permanent legislation passed by the chapter.
						\item Upon being passed, permanent legislation will be added to this appendix by the Vice President.
						\item Permanent legislation that is revoked or amended will be removed or changed in this appendix by the Vice President.
					\end{enumerate}
			\end{enumerate}
		\item Appendices may be amended or removed by the chapter in the same manner as amending the bylaws.
			\begin{enumerate}
				\item Any amendment that is not approved by the chapter by \gls{simp-maj} will be removed from its appendix.
			\end{enumerate}
	\end{enumerate}

