\chapter{Scholarship}


\section{Scholarship Standards}
	\label{member-schol-stds}
	\begin{enumerate}
		\item Once per semester, brothers and Candidates will fill out grade release forms.
		\begin{enumerate}
			\item Grade release forms must be filled out prior to the due date for midterm grades.
		\end{enumerate}

		\item Members will be evaluated according to the following criteria:\label{academic-probation}
		\begin{enumerate}
			\item Brothers on \gls{academic-probation} are required to make a  grade improvement plan with the Scholarship Chair. Any brother with a  \gls{gpa} less than 3.0 is placed on \gls{academic-probation}.

			\begin{enumerate}
				\item The grade improvement plan will be approved by the Scholarship Chair, the President, and the brother. Failure to follow the \gls{grade-imp-plan} as judged by the Scholarship Chair will result in the brother being brought up for standards.
				\label{academic-watch}

				\item A brother on \gls{academic-probation} is allowed to attend at maximum 3 social events per semester. Their responsibilities for \gls{rush} are reduced to one third of events. This brother will not be allowed to hold an elected position. \label{officer-eligibility}
				\gls{academic-probation}
			\end{enumerate}

			\item A brother shall be automatically brought up to Standards Board for an Academic Review as defined in \hyperref[academic-review]{Article XII, \autoref*{academic-review}} if:
			\begin{enumerate}
				\item They have two consecutive semester \gls{gpa}'s less than 3.0.
				\item They have a semester \gls{gpa} less than 2.75.
				%Get rid of these to keep everything numbered. Maybe make section b a seperate section
				\begin{itemize}
					\item If the brother had a previous semester \gls{gpa} also below a 2.75, the brother may be put on \gls{prob}.
				\end{itemize}
				\item They have a semester \gls{gpa} below a 2.5 and does not have a previous semester \gls{gpa} above a 3.0.
				\begin{itemize}
					\item A brother in this situation will be recommended for \gls{prob}.
				\end{itemize}
				\item Standards board is encouraged to only recommend a brother for suspenion in the most neccesary circumstances and may only do so if:
				\begin{itemize}
					\item They have two consecutive semester \gls{gpa}'s less than 2.75.
					\item They have a semester \gls{gpa} less than a 2.5.
				\end {itemize}

			\end{enumerate}

		\item If a brother is participating in a program where they do not receive a \gls{gpa} (e.g. a Co-op) and would be placed on \gls{academic-probation}:
			\begin{enumerate}
				\item They are not placed on \gls{academic-probation} that semester.
				\item The next semester in which they are not participating in such a program, they will be placed on \gls{academic-probation}.
			\end{enumerate}

		\end{enumerate}
	\end{enumerate}


\section{New Member Scholarship}
	\begin{enumerate}
		\item During the New Member program, the Scholarship Chair will meet with the New Members during a regular New Member meeting to explain the chapter \Gls{schol-program} and answer any questions they have.

		\item New Members will be held to the academic standards in \hyperref[member-schol-stds]{Article X, \autoref*{member-schol-stds}}.

		\item Candidates will be required to sign grade releases no later than 14 days of grade releases being made available.

		\item A candidate is eligible for initiation if and only if they achieved higher than a 3.0 GPA in the previous semester, or if they have a cumulative GPA of greater than 2.5. Upon receiving a Candidate's \gls{gpa}, and finding it does not meet the requirements, the Marshal shall announce this at the next regularly scheduled chapter meeting.

		\begin{enumerate}
			\item First semester freshmen are exempt from this rule.
		\end{enumerate}

		\item Any Candidate that is ineligible to be initiated will have the option to remain a Candidate.

		\begin{enumerate}
			\item Should a Candidate remain ineligible in any subsequent semester, they may remain a Candidate only with an absolute majority vote by the active chapter
		\end{enumerate}

	\end{enumerate}

\section{Privacy}
	\begin{enumerate}
		\item The President, Scholarship Chair, Alumni Advisor, and Faculty Advisor are permitted to know the \gls{gpa} of each brother.

		\item All brothers can know the names of brothers on \gls{academic-probation}.

		\item All brothers can know the names of brothers who cannot hold office due to grades.

	\end{enumerate}
